The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey

### 2020-05-16 author_list_16_May.tex
Final edits

% Author list file generated with: mkauthlist.py 0+unknown 
% mkauthlist.py -f -a order.csv -j mnras -sb author_list_07_May.csv author_list_07_May.tex

@@

@@

J.~Garc\'ia-Bellido,$^{31}$
E.~Gaztanaga,$^{32,33}$

@@

@@

@@

S.~Serrano,$^{32,33}$

@@

$^{31}$ Instituto de Fisica Teorica UAM/CSIC, Universidad Autonoma de Madrid, 28049 Madrid, Spain\\
$^{32}$ Institut d'Estudis Espacials de Catalunya (IEEC), 08034 Barcelona, Spain\\
$^{33}$ Institute of Space Sciences (ICE, CSIC),  Campus UAB, Carrer de Can Magrans, s/n,  08193 Barcelona, Spain\\

>>>>

% Author list file generated with: mkauthlist.py 0+unknown 
% mkauthlist.py -f -a DES-RET-Hosts/order.csv -s -j mnras DES-RET-Hosts/author_list_16_May.csv DES-RET-Hosts/author_list_16_May.tex

@@

P.~Fosalba,$^{31,32}$

@@

J.~Garc\'ia-Bellido,$^{33}$
E.~Gaztanaga,$^{31,32}$

@@

D.~L.~Hollowood,$^{7}$

@@

V.~Scarpine,$^{16}$

@@

S.~Serrano,$^{31,32}$

@@

$^{31}$ Institut d'Estudis Espacials de Catalunya (IEEC), 08034 Barcelona, Spain\\
$^{32}$ Institute of Space Sciences (ICE, CSIC),  Campus UAB, Carrer de Can Magrans, s/n,  08193 Barcelona, Spain\\
$^{33}$ Instituto de Fisica Teorica UAM/CSIC, Universidad Autonoma de Madrid, 28049 Madrid, Spain\\
